My title\thanks{Code and data are available at: https://github.com/AnnieYan0807/GSS-data-analysis.git.}

### 2023-03-15 outputs/paper/paper.tex
Edits to the Quarto paper

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

>>>>

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi
